---
title: "DataGeneratorMDP(2)"
author: "Monkie"
date: "11/24/2019"
output: pdf_document
---

In this program we generate more data for the CARTPOLE problem GIVEN BAYES OUTPUT AND initial input
```{r setup, include=FALSE}
list.of.packages <- c("splines", "devtools", "shinystan", "rstan", "lmerTest","gdata","foreach","rlist","doParallel")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(splines)
library(devtools)
library(shinystan)
library(rstan)
library(lmerTest)
library(gdata)
library(rlist)
library(foreach) # For parallel programming purposes
library(doParallel)
rm(list = ls())
setwd("~/Desktop/GITHUB/cartpole/cartpole")
# realdf = read.csv("cartpole.csv")
df = read.csv("DATA/data.csv")[,-1]
```

```{r}
cn = c("Step" ,"CartPos", "CartVelocity" ,"PoleAngle", "PoleVelocity" ,"Action", "Reward","FutCarPos","FutCarVel", "FutPolAng" ,"FutPolVel","ChgCarPos","ChgCarVel","ChgPolAng","ChgPolVel" )
# SET CONSTANT
n=1000000
POS = 2
CVEL = 3
ANG = 4
PVEL = 5
# MAKE HISTOGRAM TO OBSERVE DISTRIBUTION
for (i in 2:5){
  hist(df[which(df$Step==0 & df[,i]>0),i],main=paste("Initial",colnames(df)[i]),nclass=30)
}
# Observe data distribution
pairs(df[which(df$Step==0),2:5])

# Create intial state distribution
bool = matrix(sample(c(1,-1),n*3,replace = TRUE),n,3)
bool = cbind(bool,-bool[,2])
init ={}
for (i in 2:5){
  init = cbind(init,runif(n, min = min(df[which(df$Step==0 & df[,i]>0),i]), max = max(df[which(df$Step==0 & df[,i]>0),i])))
}
init = init * bool
colnames(init) = colnames(df)[2:5]
#COMPARE GENERATED INITIAL DISTRIBUTION AND INITIAL DISTRIBUTION
# pairs(init)
# pairs(df[which(df$Step==0),2:5])
```

Read Bayes generated data
```{r}
bayesdir = "BayesMLR-V1"
for (i in 12:15)  {
  assign(paste0(colnames(df)[i],"0"), read.csv(paste0(bayesdir,"/",colnames(df)[i],"BayesFit0.csv"))[,-1])
  assign(paste0(colnames(df)[i],"1"), read.csv(paste0(bayesdir,"/",colnames(df)[i],"BayesFit1.csv"))[,-1])
}
```


Make function for forpar
```{r}
play <- function(i,i2,init,B,CondtionAngle,ChgCarPos0,ChgCarVel0,ChgPolAng0,ChgPolVel0,ChgCarPos1,ChgCarVel1,ChgPolAng1,ChgPolVel1){
    j = sample(1:19000, 1)
    step = 1
    state = c(init[(i-1)*5+i2,],1)
    while (step<1000){
      if ((sum(B*state[1:4]))<0){
      state[1] = state[1] + sum(ChgCarPos0[j,] * state )
      state[2] = state[2] + sum(ChgCarVel0[j,] * state )
      state[3] = state[3] + sum(ChgPolAng0[j,] * state )
      state[4] = state[4] + sum(ChgPolVel0[j,] * state )
      } else {
      state[1] = state[1] + sum(ChgCarPos1[j,] * state )
      state[2] = state[2] + sum(ChgCarVel1[j,] * state )
      state[3] = state[3] + sum(ChgPolAng1[j,] * state )
      state[4] = state[4] + sum(ChgPolVel1[j,] * state )
      }
      j=j + 1
      step = step+1
      #If exceed some angle then we done.
      if (abs(state[3])>CondtionAngle){
        return(step)
      }
    }
    return(step)
}
```


Generate data & test generator
This test generator techinically generate a solution for the random search given the 50 datasets.
```{r}

# Make condition Angle, since we are not really sure what is the condition angle, we use a slight conservative angle where is 0.96 of the angle we have seen considered lose.
CondtionAngle = min(df$PoleAngle[which(df$Reward!=1&df$PoleAngle>0)])*0.96
n=100
# Make a matrix that cobined all the score
# Combined_score = matrix(0,n,5)
# Make a matrix that use random value Constant
Combined_B = matrix(runif(4*n,-1,1),n,4)

i=1
registerDoParallel(cores=detectCores())
partime = system.time(
# Save the final score in combined score
Combined_score <- foreach (i= 1:n,.combine = 'rbind') %:% 
  foreach (i2= 1:5,.combine = 'c') %dopar% {
     play(i,i2,init,Combined_B[i,],CondtionAngle,ChgCarPos0,ChgCarVel0,ChgPolAng0,ChgPolVel0,ChgCarPos1,ChgCarVel1,ChgPolAng1,ChgPolVel1)

}

)
registerDoParallel(cores=1)
stopImplicitCluster()

Best= which(rowMeans(Combined_score)==max(rowMeans(Combined_score)))
# Combined_B[Best,]
# Combined_score[Best,]
partime

cat("\n\nBest Policy x for Ax=B formulation\n")
Combined_B[Best,]

```

From Checkdatagenerator(2test).Rmd
Time for a regular for loop 82.061
Time for a single foreach do loop is 73.368

Our new time for 2 foreach do loop is 62.248
Our new time for 2 foreach dopar loop is 16.638

its about 4 times faster with dopar compare to do loop ------ 5 times faster compare to a regular for loop.


